\section{Introduction}
The formalization of timed regular expressions (TREs) and their equivalence to timed automata (TA) was established in the foundational paper "Timed Regular Expressions" by Eugene Asarin et al. (2001).
This paper demonstrated the construction of timed automata from timed regular expressions, which is a key focus of our research.
The ability to convert TREs to TAs allows for precise modeling and analysis of real-time systems, where timing constraints are critical.

Tools such as MONAA and UPPAAL have been developed to facilitate the application of TREs and TAs in real-world scenarios.
MONAA performs timed pattern matching on timed words by translating TREs into TAs and visualizes these automata using the DOT language for Graphviz, albeit with some conversion necessary due to custom attributes.
UPPAAL, a widely recognized tool in the verification of real-time systems, offers robust functionalities for simulating, visualizing, and verifying timed automata.
It represents systems in XML, enabling complex graph layout algorithms to enhance the visualization of timed automata.

This thesis builds upon the methods described by Asarin et al., focusing on the construction and visualization of timed automata from TREs.
We aim to enhance the visual representation of these automata through the application of advanced graph layout techniques, thereby improving their usability and comprehensibility.
By integrating the capabilities of MONAA and UPPAAL, we strive to contribute to the field of timed regular expressions and timed automata through both theoretical advancements and practical implementations