\section{Related Work}

% TRE paper: https://www-verimag.imag.fr/~maler/Papers/timed.pdf

% structure
%   meta
%   tre paper
%   monaa
%   uppaal
%   graph paper

This section aims to describe and review the literature that has been foundational for the research and work done in this paper. It contextualises the contents and contributions of this paper in the field of Timed Regular Expressions and graph layout visualisations.


The term \textit{timed regular expression} was coined in the abtly named paper "Timed Regular Expressions" from 2001, written by Eugene Asarin et al.\cite{Eugene2001}. The paper discusses the equivalence between the expressive power of timed automata\cite{ALUR1994} and timed regular expressions. To prove this equivalence, they formalise the construction of timed automata from timed regular expressions, and vice versa. In this paper, only their research on timed regular expressions and how to construct timed automata from them is used.

The aforementioned paper on timed regular expressions has been the basis for multiple studies and projects. One such project has resulted in a tool called MONAA. MONAA is a tool used for performing timed pattern matching on timed words \cite{MONAA2017}. Given a timed regular expression, MONAA translates it to an equivalent timed automata, on which the timed pattern matching is performed. Additionally, since MONAA uses the DOT language for Graphviz \cite{Graphviz} to represent their timed automata, said automata can be visualized\footnote{MONAAs automata cannot be directly visualised by Graphviz since they use custom attributes, but the developers of MONAA offer a program for converting to automata recognizable by Graphviz\cite{MONAA2017}.}.
% not sure if i should mention that the tregexs used in monaa, are not as powerful as the ones discusses in the paper?

Another aspect of this paper is finding suitable software for visualising the timed automata constructed from a given timed regular expression. A tool widely known in the field of verification of real-time systems is UPPAAL. Not only can UPPAAL model and visualise timed automata, it can also validate and verify them\cite{UPPAAL}.

UPPAAL represents their systems (collections of timed automata variables etc.) in a handful of formats, the most versatile being XML\cite{UPPAAL}. These XML files contain all the information needed to construct the automata in UPPAAL, including the positions of each individual location (conventionally named state in automata theory). This means that we can use more complex graph layout algorithms to properly visualise timed automata. The paper "Visualisation of state machines using the Sugiyama framework" by Viktor Mazetti et al. describes the theory behind and an implementation of the Sugiyama framework, also known as layered graph drawing, which will be discussed later in this paper.